Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-02 paper/paper.tex
Breakdown data

@@

@@

@@

>>>>

\begin{figure}[p]
    \centering
    \input{gen-graph-unconnected-33-breakdown}
    \caption{Clique versus constraint programming, 33\% labelled, broken down by family.}
        \label{figure:unconnected-33-breakdown}
\end{figure}

@@

\begin{figure}[p]
    \centering
    \input{gen-graph-unconnected-plain-breakdown}
    \caption{Clique versus constraint programming, undirected, unlabelled, broken down by family.}
        \label{figure:unconnected-plain-breakdown}
\end{figure}

@@

\begin{figure}[p]
    \centering
    \input{gen-graph-connected-undir33-breakdown}
    \caption{Clique versus constraint programming, connected, undirected, 33\% labelled, broken down by family.}
        \label{figure:connected-undir33-breakdown}
\end{figure}

@@

\begin{figure}[p]
    \centering
    \input{gen-graph-connected-plain-breakdown}
    \caption{Clique versus constraint programming, connected, undirected, unlabelled, broken down by family.}
        \label{figure:connected-plain-breakdown}
\end{figure}
